---
title: "Forest"
output: 
  html_document: 
    theme: journal
---

This information was collected on October 2015 in Amalfi, Antioquia (Colombia) by a group of students of Forest engineering of the Universidad Nacional de Colombia. Luisa Fernanda  Gomez, Catalina Zapata, Jonathan Mafla, Juan Pablo Gonzalez and David Triviño, we made some plots in a secundary forest, near road to Amalfi. This an information for the Forest ecology report. 

## Reading data


```{r, echo=FALSE}
setwd("C:/Users/David Esteban/Google Drive/Materias cursadas/Ecología Forestal/Informe de la salida/Datos en R")
```


```{r}
datos<-read.csv2("datos.csv")
resumidos<-read.csv2("datos_clase.csv")
biomasa<-read.csv2("Biomasa.csv")
regresion<-read.csv2("Regresión.csv")
```

## Heads of data
```{r}
head(datos)
head(resumidos)
head(biomasa)
head(regresion)
```

## Plot 
```{r}
with(regresion, plot(b_anh, xlab="Plots", ylab="Aboveground biomass"))
```

## Linear regression
```{r}
mod.lin<-lm(b_anh~n,regresion)
summary(mod.lin)
```


## Vegetation biomass

```{r}
{op <- par(mar = c(5,4.5,4,2) + 0.1)
with(biomasa, plot(AB.ha,Herbacea.ha,xlab=expression("Basal area"~(m^{2}~ha^{-1})),
                   ylab=expression("Vegetation biomass"~(Mg~ha^{-1})),ylim=c(0.2,0.4)))
par(new=T)
AB=seq(19,45,0.1)
VH<-function(AB){
        Vh=100.235*exp(-4.009^(AB^0.069))}
Vh<-VH(AB)
plot(Vh~AB,type="l",xlab="",ylab="",main="",col="blue",axes=F,ylim=c(0.2,0.4))
}
```

## Leaf litter

```{r}
Hoja<-function(AB){
        hoja=1.112*log(1+6.184*AB)
}
hoja<-Hoja(AB)


{ op <- par(mar = c(5,4.5,4,2) + 0.1)
  with(biomasa,plot(AB.ha,Hojarasca.ha,xlab=expression("Basal area"~(m^{2}~ha^{-1})),
                  ylab=expression("Leaf litter"~(Mg~ha^{-1}))))
par(new=T)
plot(hoja~AB,type="l",xlab="",ylab="",main="",col="blue",axes=F,ylim=c(5.2,6.4))}
```

## Diametric classes

```{r}
clases<-as.character(resumidos$clase)
clases=c("3","7,5","12,5","17,5","22,5","27,5","32,5","37,5","42,5","47,5","52,5","57,5")
op <- par(mar = c(5,4.5,4,2) + 0.1)
with(resumidos, barplot(Biomasa.ha,space=c(0,0),names.arg=clases,las=2,
                        ylab=expression("Biomass"~(Mg~ha^{-1})),
                        xlab=expression("Diametric classes"~(cm)), col="white"))
```

```{r}
op <- par(mar = c(5,4.5,4,2) + 0.1)
with(resumidos, barplot(AB.ha,space=c(0,0),names.arg=clases,las=2,
                        ylab=expression("Área basal"~(m^{2}~ha^{-1})),
                        xlab=expression("Clase diamétrica"~(cm)), col="white"))
```


```{r}
lim.int=c(1,seq(5,60,5))
{histograma<-hist(datos$DAP,breaks=lim.int,main="", ylab="Frecuencia", 
                 xlab="Diámetro (cm)", probability=T)
lines(density(datos$DAP),col="blue")
mtext(c(-2,0,2), side=2, las=1, at=c(-2,0,2), line=0.3, col="blue", cex=0.1)}
```


## Vegetation and leaf litter

```{r}
{
  op <- par(mar = c(5,4.5,4,2) + 0.1)
  with(biomasa, plot(AB.ha,Herbacea.ha,xlab=expression("Área basal"~(m^{2}~ha^{-1})),
ylab=expression("Biomasa"~(Mg~ha^{-1})),ylim=c(0,6.3),col="chartreuse4",pch=2))
par(new=T)
AB=seq(19,45,0.1)
VH<-function(AB){
        Vh=100.235*exp(-4.009^(AB^0.069))}
Vh<-VH(AB)
plot(Vh~AB,type="l",xlab="",ylab="",main="",col="chartreuse4",axes=F,ylim=c(0,6.3))
par(new=T)
plot(biomasa$AB.ha,biomasa$Hojarasca.ha,xlab="",ylim=c(0,6.3),
                  ylab="",col="chocolate4",pch=10,axes=F)
par(new=T)
plot(hoja~AB,type="l",xlab="",ylab="",main="",col="chocolate4",axes=F,ylim=c(0,6.3))
legend(40, 4, legend=c("Leaf litter", "Vegetation"), col = c("chocolate4", "chartreuse4"),
       pch=c(10,2))
}
```

